Benchmarking neuromorphic systems with Nengo

### 2015-11-04 paper/rebuttals.txt

> 2. Lines 320-325 are not clear.

> a) While Figure 6 does show an increase for the Nengo reference
> backend run times by removing passthrough nodes, the run time appears
> to be a 15% increase (~7x vs ~6x slower than real-time, Figure 6
> green, BG Sequence to BG Sequence *), which is approximately the same
> relative speedup as that offered by removing probes for the SpiNNaker
> backend (~1.5x to ~1.2x, Figures 6 and 7, BG sequence, blue). So,
> "significant" is a strong claim and should be clarified.

Good point. We used 'significant' colloquially here and
have therefore reworded the paragraph; it now reads:

  While passthrough nodes were removed in the basal ganglia sequence
  model for improved accuracy, it is interesting to note that speed is
  also impacted in this version of the model.  While the distilled
  backend is unaffected, both the SpiNNaker and OpenCL
  backends run faster when passthrough nodes are removed.  This result
  indicates that passthrough nodes contribute to SpiNNaker's overhead.
  The reference backend, on the other hand, runs slower, indicating
  that the computational costs of the additional connections
  introduced when removing passthrough nodes are greater than the
  costs of the passthrough nodes.

@@

We chose the range of -2 to 2
because we have used oscillators of these frequencies
in previous models. In line 219 we note that
"We test each model with parameters typically used
in large-scale models, but make these parameterized models
available ... for those who wish to explore additional cases."
The parameter is trivial to change, up to an upper frequency limit
which depends on the properties of the neurons in use;
we would be happy to show results for a different set of frequencies
if that would be preferable.

> 4. Table 1, the compliance of the four backends, should be explained
> more fully in the caption. The levels of coverage are surprisingly low
> given that all backends are able to perform the main cognitive-level
> tasks; common failure cases (e.g., missing neuron models) should be
> mentioned to show why these are not necessary.

The caption for the compliance table (which now includes all 5 backends)
has been updated. It now reads:

  Compliance of the five backends. Compliance is the number of
  functional tests passed by a particular backend. We have divided
  these tests into tests parameterized by neuron type, and those not
  parameterized.  Non-parameterized tests are either designed to work
  with only one neuron type, or use leaky integreate-and-fire (LIF)
  neurons, which are implemented on all backends. For parameterized
  tests, we have separated the compliance for those tests using LIF
  neurons, which all backends implement, and for any additional neuron
  types implemented. Since there are 31 parameterized tests, the
  maximum compliance is 31 times the number of neuron types
  implemented.  The reference backend implements three additional
  neuron types, while OpenCL, and Distilled, implement one
  additional neuron type, and SpiNNaker only implements LIF neurons.

@@

Additionally, a paragraph explaining common failure cases
is included in the main text in lines 309-319. It reads:

  It should be noted that these test suites are being run on the
  distilled and SpiNNaker backends for the first time in
  this study.  In other words, these results are the first objective
  interrogation of each backend's feature set.  In many cases, tests
  failed by backends are tests of features recently added to Nengo,
  such as stochastic processes for injecting current noise.  As such,
  we expect compliance on all backends to rise quickly as backend
  developers implement these new features.  The OpenCL backend has
  higher compliance in large part because it is developed by the same
  group that develops the reference backend.  However, there are some
  notable features missing from some backends, such as learning
  through plasticity rules applied to neuron-to-neuron connections,
  and implementation differences, such as one timestep delays on
  connections with no synaptic filter, that may remain even when
  backends are brought up to date with the reference implementation.
  It is likely that tests will be rewritten in the future to allow
  some implementation differences if they do not affect simulation
  accuracy.

@@

> - Table 2 is referenced before Table 1 in the text - their order
>   should be changed

Thank you, this has been corrected.

5. Other comments on the results.
---------------------------------

> I found the description of the Figures on accuracy too short. Even
> if the accuracy results themselves are not the main focus of the
> article, some more explanations for the results should be given. In
> particular, in Figs. 1 and 2, why does the Nengo reference backend
> show a significantly higher variability than the
> distilled backend? In Figs. 3 and 4, where do the deviations in the
> SpiNNaker backend come from (my first guess would be the employed
> 1ms time step, which is larger than the 0.1ms typically used in
> software simulators)?

@@

We have added additional details in the section 4.2 on accuracy.
These additional details are listed below.

Unfortunately, we do not have a satisfying explanation
for why the reference backend shows higher variability than
the distilled backend.
We discuss this briefly in the additional details below
and have added a sentence to the discussion
indicating that we will examine this result in the future
(lines 395-397: "We also plan to investigate
why the reference and OpenCL backends
have higher variability than other backends on
the simple feedforward models.")

@@

We are still in the progress of investigating the deviations
in the SpiNNaker backend; however, we are collaborating with
the SpiNNaker group to improve accuracy on these examples.
The 1 ms time step is not the issue here, however,
as all of the backends tested use a 1 ms time step.

Figure 1:

  The distilled backend has the least variability and
  the SpiNNaker backend has the most variability, though the median
  RSME is the same across all backends.  One driver of these
  differences is in how each backend handles ensembles operating near
  the edge of their representational range (i.e., the radius of the
  ensemble).  The outlier with highest RMSE represents a model
  instance in which the static vector target was at the extreme of the
  representational range; the SpiNNaker backend's relatively high RMSE
  on this example indicates that it may not perform as well as other
  backends in this situation.  The SpiNNaker backend uses signed fixed
  point numbers with 16 digits before the decimal point, and 15 digits
  after the decimal point; accuracy could be improved by optimizing
  the backend's internal calculations to use as many digits as
  possible.  For all backends, accuracy could be improved by
  increasing the representational range and increasing the number of
  evaluation points generated when solving for decoding weights.

@@

Figure 2:

  Again, it is likely that performance at the extremes of the
  representational range is responsible for the SpiNNaker backend's
  reduced accuracy, though we have not investigated this in detail.
  This benchmark also suggests that the reference and OpenCL backends
  have more variability than the distilled backend.
